Flowchart of Current Algorithm

### 2009-05-04 docs/flowchart/flowchart.tex
more updates, mostly language

\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so we just compute the new pressure directly.  The
problems we have seen with enforcing HSE directly have to do with the roundoff
error that accumulates, causing the temperature computed from the EOS to drift.

@@

\item[Step 1.] {\em Define the average expansion at time $t^\nph$ and the new $w_0.$}

@@

%--------------------------------------------------------------------------
% STEP 2
%--------------------------------------------------------------------------
\item[Step 2.] {\em Construct the provisional edge-based advective velocity}, $\uadvone$.\\

@@

%--------------------------------------------------------------------------
% STEP 6
%--------------------------------------------------------------------------
\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}

@@

%--------------------------------------------------------------------------
% STEP 7
%--------------------------------------------------------------------------
\item[Step 7.] {\em Construct the final edge-based advective velocity}, $\uadvtwo$.

@@

The initial perturbational pressure also needs to be determined for
use in steps 2, 7 and 11. 
This is done through a second iterative procedure which follows the
time advancement algorithm as described in steps 1-11 in 
\S~\ref{Sec:Time Advancement Algorithm}.  
The user specifies the number of iterations, 
$N_{\rm iters}^{\pi},$ in this second step of the initialization procedure.
The details for both iterations are given below.\\

>>>>

\item Should we eliminate {\bf Advect Base Pressure} entirely, and instead directly
enforce HSE after {\bf Correct Base}?  {\bf Advect Base Pressure} was just a fancy
way of enforcing HSE anyway, so we just compute the new pressure directly.  The
problems we have seen with enforcing HSE directly have to do with the roundoff
error that accumulates, causing the temperature computed from the EOS to drift.
However, using {\bf Advect Base Pressure}, the latest version of {\bf test\_basestate}
does not work after some bug fixes.

@@

\item[Step 1.] {\em Define the provisional time-centered expansion, $S^{n+\myhalf,\star}$, 
base state velocity, $w_0^{n+\myhalf,\star}$, and base state velocity forcing.}

@@

%--------------------------------------------------------------------------
% STEP 2
%--------------------------------------------------------------------------
\item[Step 2.] {\em Construct the provisional time-centered advective velocity on 
edges, $\uadvone$.}

@@

%--------------------------------------------------------------------------
% STEP 6
%--------------------------------------------------------------------------
\item[Step 6.] {\em Define the final time-centered expansion, $S^{n+\myhalf}$, 
base state velocity, $w_0^{n+\myhalf}$, and base state velocity forcing.}

@@

%--------------------------------------------------------------------------
% STEP 7
%--------------------------------------------------------------------------
\item[Step 7.] {\em Construct the final time-centered advective velocity on 
edges, $\uadvtwo$.}

@@

The initial perturbational pressure also needs to be determined for
use in steps 2, 7 and 11. 
This is done through a second iterative procedure which follows the
time advancement algorithm as described in steps 1-11 in 
\S \ref{Sec:Time Advancement Algorithm}.  
The user specifies the number of iterations, 
$N_{\rm iters}^{\pi},$ in this second step of the initialization procedure.
The details for both iterations are given below.\\
